From Big Data to Big Displays\\ High-Performance Visualization at Blue Brain

### 2017-05-29 paper.tex
Draft conclusion

\section{C++ Messaging and Services}

@@

Brayns will become the integrative visualizer

Messaging enables surprising new use cases

Tiled display walls are cheap and ready for new ways of working

>>>>

\section{Messaging and Service Architecture}

@@

We have presented a modular visualization architecture for large data
visualization over a wide range of use cases, glued together by a modern and
easy to use messaging infrastructure. This ecosystem allows us to flexibly
support novel use cases, while pushing novel visualization capabilities,
providing Blue Brain with a competitive visualization infrastructure. Messaging
and remote APIs not only surprised us in their versatility and ease of
integration with other tools, but have still a significant potential for future
exploration of classical visualization software. Interactive raytracing is the
rendering algorithm for us, and Brayns is becoming the integration point for our
domain-specific visual applications and algorithms. Tiled display walls are
affordable for a large set of institutions, and coupled with our open source
TIDE software create new ways of truely collaborative work. TIDE, together with
cheaper visualization hardware, will evolve in the future towards a seamless
integration of immersive visualization.
